\documentclass{article}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{microtype}
\usepackage[colorinlistoftodos]{todonotes}
\pagestyle{empty}

\title{Stable Matching Report}
\author{Isak och Erik}

\begin{document}
  \maketitle

  \section{Results}

  Correct solutions, all in all about 27 seconds to run check\_solutions using pypy. The parsing takes the most time by far, just about 90\% of execution time is parsing.
  Largest input takes about 2 seconds using.

  \section{Implementation details}

  We parse using list comprehension, splitting input into two dictionaries of students and companies. We loop over a list of unmatched students,
  and iterate over companies for each unmatched student in the list. 

  \section{Lab questions}

  \subsection{Why does your algorithm obtain a stable solution?}

  When the algorithm terminates, no student company pair will prefer each other more than the final match. 

  \subsection{Could there be other stable solutions?}

  There is a possibility for other stable solutions, such as solutions with overall less satisifed pairs.

  \subsection{What is the time complexity and why?}

  The time complexity is $O({n}^2)$. Setting up the datastructures takes $O(n)$, and the algorithm itself also takes $O({n}^2)$.

  \subsection{Are there any applications of the algorithm (as it is or in a slightly shifted verison)?}

  Dating app hinge uses the algorithm. 
  Planning shifts -- jobba på bruged




\end{document}
